Syntax and Semantics of Abstract Binding Trees

### 2015-11-11 paper.tex
formatting
Fix possible typo?
@freebroccolo was this intentional? If so, I'll revert
Revert "Fix possible typo?"
This reverts commit f4a26616a843bec5d6be0030506e87daae804cf1.
[paper] clarify some details

By the Grothendieck construction
$\Iso{\Grothendieck{}{\Operators}}{\Comma{*}{\Operators}}$ we have a category
of elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are diagrams:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\Pair{\Upsilon}{a}}
      \arrow[r, "\Pair{\rho}{f}", swap]
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, sep = small, ampersand replacement = \&]
    \& *
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]
We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\to\SCtx\times\Discrete{\Arities}}$
in which they reside:
\begin{alignat*}{3}
  &{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}&&\,\mathrel{\ {{:}}}\,&&\SCtx\times\Discrete{\Arities}\to\Sets\\
  &{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}&&\,=\,\ && %
    \{\ \ \Member{\vartheta}{\Pair{\Upsilon}{a}}\ \ |\ \
    {\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
    \Pair{\Upsilon}{a}\,\}
\end{alignat*}

@@

For instance, consider the $\lambda$-calculus with a single sort, $\SortExp$; we
give its signature $\Sigma_{\lambda}$ by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\mathtt{lam}}{
    \MkArity{\MkValence{}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathtt{ap}}{
    \MkArity{
      \MkValence{}{}{\SortExp},
      \MkValence{}{}{\SortExp}
    }{\SortExp}
  }
\end{gather*}
These rules correspond to objects of $\Grothendieck{}{{\Operators}_{\lambda}}$ and we
collect their fibers into sets of operators:
\begin{alignat*}{5}
{\pi_{{\Operators}_{\lambda}}}^{-1}&\Pair{\Upsilon}{{\MkArity{\MkValence{}{\SortExp}{\SortExp}}{\SortExp}}}\quad&&=
  &&\quad\MkSet{\mathtt{lam}}\\
{\pi_{{\Operators}_{\lambda}}}^{-1}&\Pair{\Upsilon}{\MkArity{\MkValence{}{}{\SortExp},\MkValence{}{}{\SortExp}}{\SortExp}}\quad&&=
  &&\quad\MkSet{\mathtt{ap}}\\
{\pi_{{\Sigma}_{\lambda}}}^{-1}&=\bigcup_{\Pair{\Upsilon}{a}}{{\pi_{{\Operators}_{\lambda}}}^{-1}{\Pair{\Upsilon}{a}}}\quad&&=
  &&\quad\MkSet{\mathtt{lam},\ \mathtt{ap}}\\
\end{alignat*}
So far, we have made no use of symbols and parameters; however, consider the
extension of the calculus with assignables (references):

>>>>

By the Grothendieck construction
$\Iso{\Grothendieck{}{\Operators}}{\Comma{*}{\Operators}}$ we have a category of
elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are paired
diagrams:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\Pair{\Upsilon}{a}}
      \arrow[r, "\Pair{\rho}{f}", swap]
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, sep = small, ampersand replacement = \&]
    \& *
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]
We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\to\SCtx\times\Discrete{\Arities}}$
in which they reside:
\begin{alignat*}{3}
  &\IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}&&\,\mathrel{\ {{:}}}\,&&\IMode{\SCtx\times\Discrete{\Arities}\to\Sets}\\
  &\IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}&&\,=\,\ && %
    \OMode{%
      \MkSet{
        \vartheta\in\Pair{\Upsilon}{a}
        \mid
        {\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
        \Pair{\Upsilon}{a}
      }
    }
\end{alignat*}

@@

For instance, consider the $\lambda$-calculus with a single sort, $\SortExp$; we
give its signature $\Sigma_{\lambda}$ by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\mathtt{lam}}{
    \MkArity{\MkValence{}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathtt{ap}}{
    \MkArity{
      \MkValence{}{}{\SortExp},
      \MkValence{}{}{\SortExp}
    }{\SortExp}
  }
\end{gather*}
These rules correspond to objects of $\Grothendieck{}{{\Operators}_{\lambda}}$ and we
collect their fibers into sets of operators:
\begin{alignat*}{5}
\IMode{{\pi_{{\Operators}_{\lambda}}}^{-1}}&\IMode{\Pair{\Upsilon}{{\MkArity{\MkValence{}{\SortExp}{\SortExp}}{\SortExp}}}}\quad&&=
  &&\quad\OMode{\MkSet{\mathtt{lam}}}\\
\IMode{{\pi_{{\Operators}_{\lambda}}}^{-1}}&\IMode{\Pair{\Upsilon}{\MkArity{\MkValence{}{}{\SortExp},\MkValence{}{}{\SortExp}}{\SortExp}}}\quad&&=
  &&\quad\OMode{\MkSet{\mathtt{ap}}}\\
\IMode{{\pi_{{\Sigma}_{\lambda}}}^{-1}}&\triangleq\IMode{\bigcup_{\Pair{\Upsilon}{a}}{{\pi_{{\Operators}_{\lambda}}}^{-1}{\Pair{\Upsilon}{a}}}}\quad&&=
  &&\quad\OMode{\MkSet{\mathtt{lam},\ \mathtt{ap}}}\\
\end{alignat*}
So far, we have made no use of symbols and parameters; however, consider the
extension of the calculus with assignables (references):
